Maxwell's Silver Hammer, summarized:\\ On the application of pulsed microwave acoustic resonant viral inactivation

### 2020-07-23 documents/pamphlet.tex
gosh writing papers is addictive, have to stop

\title{Maxwell's Silver Hammer, briefly:\\ On the application of pulsed microwave acoustic resonant viral inactivation}

@@

This is a heavily condensed version of a (hideously unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.

I think it is important that you doubt and scrutinize everything written. This hinges on minutia and

@@

\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017}) appear to establish that the net charge, mass, and envelope stiffness of a few species of viruses supports a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz.

@@

Results seem to indicate that any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 10 ns will be sterilized. This is not a particularly demanding requirement.

>>>>

\title{Maxwell's Silver Hammer, summarized:\\ On the application of pulsed microwave acoustic resonant viral inactivation}

@@

This is a heavily condensed version of a (hideously unfinished) paper at \href{https://www.github.com/0xDBFB7/covidinator/documents/paper.pdf}{\faGithub/0xDBFB7/covidinator}.\footnote{Assign blame to Daniel Correia [TODO affiliation] \orcidlink{0000-0002-9353-0216}}

Both the microwave and dosimetric components \footnote{field field?} appear to be unusually sensitive to experimental design and exceptionally prone to artifacts that cause false positive results: \cite{Microwave1982} $\neq$ \cite{Resonances1987}, \cite{Effects1985a} $\neq$ \cite{Cytogenetic1986}, \cite{Comprehensive2018}. Though the cited articles have taken care to avoid these effects, is possible that none of what is discussed below actually exists.

@@

\cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{A great many papers are involved.} appear to establish that the net charge, mass, and envelope stiffness of a few species of viruses supports a weak resonance mode in the microwave spectrum, with a peak at roughly 8 GHz.

@@

Results seem to indicate that any region with a power density in the 7 to 9 GHz band greater than 300\Wsqm \ for 10 ns will be sterilized. This is not a particularly demanding requirement. We provide a reference design that costs \$3 in prototype quantities.
